An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-03-10 poly-embed-journal/poly-embed-journal.tex
Revisiting Claim 6

Now we can observe a set of normals $\V'$ generating faces whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
\jessie{Left off here}
\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For $\V' \subseteq \V$, we have
	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
\end{claim}
\begin{proof}
	\jessiet{Revisit... not tracking, but that could just be a slow morning on my end.}
	For any $v \in \V$, define $F_v := H_v \cap \hyp(g_\V)$.
	We would like to show
	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption. %apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

@@

	($\implies$) 
	Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
	Fix $x \in \reals^\Y_+$.
	Since $\V' \subseteq \V$, and $G = \cap (\H_\Y \cup \H_\V)$, we immediately have $G \subseteq \cap (\H_\Y \cup \H_{\V'})$.
	Therefore, we just need to show the other direction of inclusion.
	%  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
	$(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Lemma~\ref{lem:x-nonneg-orthant-iff-intersection-HY}, so it is left to show that $(x,c) \in \cap \H_{\V'}$, which yields the desired result.
	First, $(x,c) \in \cap \H_{\V'}$ implies $(x,c) \in H^+_{v'}$ for all $v' \in \V'$.
	This implies $c \leq \inprod{v'}{x}$ for all $v' \in \V'$.
	By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, there exists a $v' \in \V'$ such that $(x,g_\V(x)) \in F_{v'}$, and $\inprod{v'}{x} = g_\V(x)$.
	Therefore, we have $c \leq \inprod{v'}{x} = g(x)$, and $(x,c) \in G$ follows since $G$ is the hypograph of $G$.

	%\raf{Want to show $c \leq g(x)$, then done by def $G$}
	%\raf{Now $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'} \implies c \leq \inprod{v'}{x} = g(x) \implies (x,c) \in G$}

	% ...$\leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.

	($\impliedby$)
	$G = \cap (\H_\Y \cup \H_{\V'})$ if and only if $G = \cap \H_{\V'}$ when restricting to $x \in \reals_+^\Y$.
	This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap G = F_{v'} \implies x \in \pi(F_{v'})$.
	As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.

>>>>

Now we can observe a set of normals $\V'$ generating faces whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
\jessie{Left off here}
\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
	Consider $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-finite} or $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For $\V' \subseteq \V$, we have
	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
\end{claim}
\begin{proof}
	\jessiet{Revisit- just rewrote (Mar 10)}
	For any $v \in \V$, define $F_v := H_v \cap \hyp(g_\V)$.
	%We would like to show $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption. %apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

@@

	($\implies$) 
	For contraposition, suppose $\V^* \not \subseteq \V'$.
	Then $\exists v \in \V^* \setminus \V'$.
	Observe that $\V^*$ is unique and irredundant (by assumption) and $\pi(F^{\hyp(g_\V)}_v)$ is full-dimensional in $\reals^\Y_+$ by Corollary~\ref{cor:anything-gen-G-subset-Hstar} and Claim~\ref{claim:pi-preserves-dim}.
	Moreover, $\pi(F_v^{\hyp(g_\V)}) \not \in \cup_{v' \in \V'} \pi(F_v^{\hyp(g_\V)})$, which implies $\cup_{v' \in \V'} \pi(F_v^{\hyp(g_\V)}) \neq \cup_{v^* \in \V^*} \pi(F_{v^*}^{\hyp(g_\V)}) = \reals^\Y_+$.

%Commented out March 10 2022 and replaced with above- Jessie
%	Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
%	Fix $x \in \reals^\Y_+$.
%	Since $\V' \subseteq \V$, and $G = \cap (\H_\Y \cup \H_\V)$, we immediately have $G \subseteq \cap (\H_\Y \cup \H_{\V'})$.
%	Therefore, we just need to show the other direction of inclusion.
%	%  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
%	By Lemma~\ref{lem:x-nonneg-orthant-iff-intersection-HY} we have $(x,c) \in \cap \H_\Y$ for all $c \in \reals$, so it is left to show that $(x,c) \in \cap \H_{\V'}$, which yields the desired result.
%	First, $(x,c) \in \cap \H_{\V'}$ implies $(x,c) \in H^+_{v'}$ for all $v' \in \V'$.
%	This implies $c \leq \inprod{v'}{x}$ for all $v' \in \V'$.
%	By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, there exists a $v' \in \V'$ such that $(x,g_\V(x)) \in F_{v'}$, and $\inprod{v'}{x} = g_\V(x)$.
%	Therefore, we have $c \leq \inprod{v'}{x} = g_\V(x)$, and $(x,c) \in \hyp(g_\V)$ follows.
%	
%	%\raf{Want to show $c \leq g(x)$, then done by def $G$}
%	%\raf{Now $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'} \implies c \leq \inprod{v'}{x} = g(x) \implies (x,c) \in G$}
%	
%	% ...$\leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.

	($\impliedby$)
	Since $\V^* \subseteq \V'$, we immediately have \jessie{todo...}
%	$\hyp(g_\V) = \cap (\H_\Y \cup \H_{\V'})$ if and only if $\hyp(g_\V) = \cap \H_{\V'}$ when restricting to $x \in \reals_+^\Y$.
%	This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap \hyp(g_\V) = F_{v'} \implies x \in \pi(F_{v'})$.
%	As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.
